---
title: "Lab1"
author: "Jo Starenky"
date: "2024-09-16"
output: "github_document"
---

# Load Packages
```{r}

library(haven)
library(tidyr)
library(ggplot2)
library(datasauRus)
library(dplyr)

```

# First look of descriptive statistics 
```{r}

datasaurus_dozen %>% 
  group_by(dataset) %>%
  dplyr::summarize(mean_x    = mean(x),
      mean_y    = mean(y),
      std_dev_x = sd(x),
      std_dev_y = sd(y),
      corr_x_y  = cor(x, y)
    )


```

# Introduce GGplot
```{r}

ggplot(datasaurus_dozen, aes(x = x, y = y, colour = dataset))+
    geom_point() + facet_wrap(~dataset)

dino<- datasaurus_dozen %>%
  filter(dataset == "dino")

ggplot(dino, aes(x = x, y = y))+
  geom_point (color="#FF13F0") + theme_void() + labs(title = "Hi, I'm a dino!") + theme(plot.title = element_text(hjust = 0.5, face = "bold", size = 20, color = "pink"))




```


# Q1: What is the function of facet wrap? In what situation do you think you will use this function? 
 Facet wrap is a function that can be used to help separate things; for example, in a situation where we have multiple independent variables, we can use facet wrap to plot by condition
 

# Q2: The means, standard deviations, and correlations are pretty much the same, but the data pattern looks very different for each dataset. What is the implication here? 
This implies that descriptive statistics do not always tell the whole story, and it is crucial to always visualize the data in order to paint the full picture.